Formalizing Commutative Algebra in Coq: \\ Nakayama's Lemma\thanks{Source code for this work is available on the following site: \url{https://github.com/ku-sldg/algebra}}

### 2022-11-13 nakayama/paper.tex
Minor updates based on issues being addressed

\emily[inline]{Emily: It would be more consistent to require a ring to contain
$1$ in general, instead of adding this to the axioms of a commutative ring.
After thinking for a while, I think it is a good idea to make this change in
the code, and then here to match. Drew, does this sound OK?}

@@

The set of integers also forms a \emph{ring} due to its properties of
multiplication. It is closed under this binary operation, which satisfies
associativity, and the distributive law governing the compatibility of addition
and multiplication holds. Even more, the integers form a
\emph{commutative ring} since $n \cdot m = m \cdot n$ for all integers $n$ and
$m$. We require commutative rings to contain a \emph{multiplicative identity},
and $1 \in \mathbb{Z}$ is such an element since $n \in \mathbb{Z}$ one has
$n \cdot 1 = 1 \cdot n = n$.

@@

\subsection{Our Algebraic Hierarchy}
\begin{figure}[t]
  \caption{The hierarchy of our algebraic structures}
  \includegraphics[width=.4\textwidth]{algebraic-structures.pdf}
  \centering
\end{figure}
\todo[inline]{To do:  Double check source code to verify whether the hierarchy
figure should be altered (subobjects, quotients, finitely generated modules,
local rings, etc.) It looks good to Drew.}

@@

Moving onward, we formalized the structure of a ring, which has two binary
operations: addition, which must be commutative, and multiplication, which need
not be commutative in general. Next we defined the structure of a commutative
ring, further requiring commutativity of multiplication, as well as a
multiplicative identity. At this point, we formalized the notion of an ideal of
a commutative ring, a subgroup of the ring under addition that satisfies the
absorption property under multiplication, i.e., \(r a\) is in the ideal for
every element \(a\) of the ideal, and every element \(r\) of the commutative
ring. We also used this to formalize the notion of a quotient ring $R/I$, where
$I$ is an ideal of a commutative ring $R$.

\emily[inline]{It would be nice to differentiate between our structures that
  are typeclasses (e.g., {\ttfamily Ideal}), and other definitions (e.g.,
  {\ttfamily maximal ideal})}

@@

\emily[inline]{Emily:  Unfortunately, I think we need to update naming
  conventions since in mathematics, ``vector'' is reserved for an element of a
  vector space over a field, rather than an element of an arbitrary module.  So
  this could cause confusion.  Similar with ``basis,'' which is especially
  tricking since two different generating sets of a finitely generated module
  can have different sizes, but all bases of a vector space have the same
  cardinality, and an element of a module can typically be written as a scalar
  combination in multiple ways, while bases are linearly independent.  I've
  proposed a rewrite of the blue paragraph right above it.  Drew, can you
  double check it for accuracy with respect to the code? 
}
\emily[inline]{We'll also need to update the code.  I think {\ttfamily vectors}
  should be something like {\ttfamily scalar-combinations}, and
  {\ttfamily basis} something like {\ttfamily generating-set}. 
}

@@

\textcolor{blue}{Here we needed to formalize the notion of linear combinations
  of coefficients and module vectors. This was done by dependently typed
  vectors, i.e., lists parameterized by their length. Because there is an
  overload of the term ``vector'', we will use that term to refer to module
  vectors, and use the term ``list'' to mean length-parameterized lists. As we
  don't use the simpler kind of lists, this avoids any name collisions. A
  finitely generated module is like the vector space \(\mathbf{R}^{n}\) in that
  there are finitely many vectors which can generate all other vectors, for
  \(\mathbf{R}^{n}\) one such collection of generators are
  \(\mathbf{e}_{1} = \begin{pmatrix} 1 & 0 & 0 & \cdots & 0\end{pmatrix}^{T}\),
  \(\mathbf{e}_{2} = \begin{pmatrix} 0 & 1 & 0 & \cdots & 0\end{pmatrix}^{T}\),
  \textellipsis,
  \(\mathbf{e}_{n} = \begin{pmatrix} 0 & 0 & 0 & \cdots & 1\end{pmatrix}^{T}\).
  In our code, \texttt{M} is the type of module elements, \texttt{R} is the
  type of ring elements which act as coefficients, and \texttt{t A n} is a list
  whose elements are of type \texttt{A} and whose length is \texttt{n}.
}

@@

\subsection{Building the Formal Proof}
Beyond formalizing the relevant structures from higher algebra, we also
formally establish some basic theory. For instance, a \emph{unit} of a
commutative ring $R$ is an element $x \in R$ with a multiplicative inverse,
i.e., an element $x^{-1} \in R$ for which $x \cdot x^{-1}$ is the
multiplicative identity $1 \in R$.

>>>>

@@

The set of integers also forms a \emph{ring} due to its properties of
multiplication. It is closed under this binary operation, which satisfies
associativity, and the distributive law governing the compatibility of addition
and multiplication holds.  We require rings to contain a \emph{multiplicative identity},
and $1 \in \mathbb{Z}$ is such an element since $n \in \mathbb{Z}$ one has
$n \cdot 1 = 1 \cdot n = n$. 
Even more, the integers form a
\emph{commutative ring} since $n \cdot m = m \cdot n$ for all integers $n$ and
$m$.

@@

\subsection{Building our Algebraic Hierarchy}
\begin{figure}[t]
  \caption{The hierarchy of our algebraic structures}
  \includegraphics[width=.4\textwidth]{algebraic-structures.pdf}
  \centering
\end{figure}

@@

Moving onward, rings are the next step in our algebraic heirarchy; a ring has two binary
operations: addition, which must be commutative, and multiplication, which need
not be commutative in general. Next, we formalized the definition of a commutative
ring, further requiring commutativity of multiplication, as well as a
multiplicative identity. At this point, we formalized the notion of an ideal of
a commutative ring, a subgroup of the ring under addition that satisfies the
absorption property under multiplication, i.e., \(r a\) is in the ideal for
every element \(a\) of the ideal, and every element \(r\) of the commutative
ring. We also used this to formalize the notion of a quotient ring $R/I$, where
$I$ is an ideal of a commutative ring $R$.

@@

%\emily[inline]{Emily:  Unfortunately, I think we need to update naming
%  conventions since in mathematics, ``vector'' is reserved for an element of a
%  vector space over a field, rather than an element of an arbitrary module.  So
%  this could cause confusion.  Similar with ``basis,'' which is especially
%  tricking since two different generating sets of a finitely generated module
%  can have different sizes, but all bases of a vector space have the same
%  cardinality, and an element of a module can typically be written as a scalar
%  combination in multiple ways, while bases are linearly independent.  I've
%  proposed a rewrite of the blue paragraph right above it.  Drew, can you
%  double check it for accuracy with respect to the code? 
%}
%\emily[inline]{We'll also need to update the code.  I think {\ttfamily vectors}
%  should be something like {\ttfamily scalar-combinations}, and
%  {\ttfamily basis} something like {\ttfamily generating-set}. 
%}

@@

@@

\subsection{Constructing the Formal Proof}
Beyond formalizing the relevant structures from higher algebra, we also
formally establish some basic theory. For instance, a \emph{unit} of a
commutative ring $R$ is an element $x \in R$ with a multiplicative inverse,
i.e., an element $x^{-1} \in R$ for which $x \cdot x^{-1}$ is the
multiplicative identity $1 \in R$.
